### 2010-07-02 paper/IIWAS2010/content/system_arch.tex
Modified the example based on the new figure

Morpheus uses an ontology that contains classes of a particular realm of interest. Each leaf node in the ontology is associated with a corpus of words belonging to a class.  For example, we have constructed an automotive ontology containing classes relevant to the automotive realm. This ontology provides a structure for reference in the following sections.

@@

In addition, we evaluate Latent Dirichlet Allocation (LDA) to identify latent topics of the documents in a corpus \cite{Blei2003latentdirichlet}.  LDA is Bayesian model that represents a document in the corpus by distributions over topics, and a topic itself is a distribution over all  terms in the corpus.  For example, for the Wikipedia pages, the latent topics reflect the thematic structure of the pages. Thus, LDA can discover relevant topic proportions in a document using posterior inference \cite{Blei2003latentdirichlet}. Additionally, given a text document, using LDA we could tag related documents by matching the similarity over the estimated topic proportions, which is useful in the ontology and corpora building.  Due to its fully generative semantics, even at the level of documents, LDA could address the drawbacks (such as dimensionality and failure in finding the discriminative set of words for a document) of frequency based approaches such as TF-IDF, LSI, and pLSI.

@@

The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path-finder answering a question. The path-finder also uses the tool to identify ontological categories associated with search terms. Morpheus stores the query together with its terms and categories as an SSQ (Table \ref{tab:ssq_example}). Using the QRR, the path-finder is also able to identify where answers can be found within traversed pages.

@@

\begin{table}
\scalebox{0.76}{
	\rowcolors{1}{white}{white}
	\begin{tabular}{|r|l|l|l|l|l|l|l|l|}
		\hline
		\textbf{Terms} & 1997 & Toyota & Camry & V6 & size & tires \\
		\hline
		\textbf{Input} & Date & Manufacturer & Model & Engine & &  \\
		\textbf{Output} & & & & & Measurement & Part \\
		\hline
	\end{tabular}
	}
	\caption{An SSQ for the question: ``A 1997 Toyota Camry V6 has what size tires?"  Cells represent categories}
	\label{tab:ssq_example}
\end{table}

The \emph{Query Resolution Method} (QRM) is a data structure that models the
question answering process. A QRM represents a generalized executable realization of the search process that the path-finder followed. The QRM is able to reconstruct the page search path followed by the path-finder. Each QRM contains an \emph{ontological realm}, an SSQ, and information to support the query answering process. For each dynamic page, it stores the list of inputs to the URL such as form inputs and the possible reference outputs (highlighted portions of the web page).

@@

Queries inserted by path-followers take a different approach. The Morpheus search system parses, tags, and processes the queries in order to pull important terms. The system then assigns the most probable realm to the query using $p(realm|term)$ priors calculated from realm-specific corpora. Once the realm is assigned, an ontology search is performed to assign classes to the terms. An SSQ is constructed and the system attempts to match this SSQ to a query path created by a path-finding user. Rather than matching terms, the goal is to match input and output classes, since the paths can potentially answer similar queries.

@@

% Algorithm 1: figure  
\begin{figure}[t]
	\centering
%\includegraphics[width=85mm]{../img/automotive_ontology.eps}
\includegraphics[width=85mm]{automotive_ontology.eps}
\caption{An abbreviated man-made automotive ontology - arrows represent inheritance relationships between the ontological classes.}
\label{fig:automotive_ontology}
\end{figure}

Suppose we want to find the category divergence between \textit{Sedans}
and \textit{Trucks} (Figure \ref{fig:automotive_ontology}). 
\textit{Sedans} is the subcategory of \textit{Cars}, and \textit{Trucks}
is the subcategory of \textit{Automobiles}. Therefore, the least common ancestor ($C$)
for these twoThis section presents ontology and copora, Query processing, ranking queries, and the query resolution mechanism. categories is \textit{Automobiles}. In addition, the tree height \textit{h = 4}.
So, the normalized divergence $cd$\textit{(Sedans, Trucks)} is \textit{7/12}
that is calculated from \textit{d(Sedans, Root) = 4}, \textit{d(Sedans, Automobiles) = 2}, and \textit{d(Trucks, Automobiles) = 1}.

>>>>

Morpheus uses an ontology that contains classes of a particular realm of interest. Each leaf node in the ontology is associated with a corpus of words belonging to a class.  For example, we have constructed a vehicular ontology containing classes relevant to the vehicular realm. This ontology provides a structure for reference in the following sections.

@@

In addition, we evaluate Latent Dirichlet Allocation (LDA) to identify latent topics of the documents in a corpus \cite{Blei2003latentdirichlet}.  LDA is Bayesian model that represents a document in the corpus by distributions over topics, and a topic itself is a distribution over all  terms in the corpus.  For example, for the Wikipedia pages, the latent topics reflect the thematic structure of the pages. Thus, LDA can discover relevant topic proportions in a document using posterior inference \cite{Blei2003latentdirichlet}. Given a text document, we tag related documents by matching their similarity over the estimated topic proportions, assisting in ontology and corpora construction.  Due to its fully generative semantics, this usage of LDA could address drawbacks of frequency based approaches (e.g. TF-IDF, LSI, and pLSI) such as dimensionality and failure to find the discriminative set of words for a document. %of frequency based approaches.% such as TF-IDF, LSI, and pLSI.

@@

The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path-finder answering a question. The path-finder also uses the tool to identify ontological categories associated with search terms. Morpheus stores the query together with its terms and categories as an SSQ.  Table \ref{tab:ssq_example} is an example showing the SSQ model of the query ``A 1997 Toyota Camry V6 has what size tires?". The SSQ in Table \ref{tab:ssq_example} is said to be \emph{qualified} because the classes associated with its terms have been identified. Using the QRR, the path-finder is also able to identify where answers can be found within traversed pages.

@@

%% TODO - we need the table here
\begin{table}[h]
\scalebox{0.76}{
	\begin{tabular}{|r|l|l|l|l|l|l|l|l|}
		\hline
		\textbf{Terms} & 1997 & Toyota & Camry & V6 & size & tires \\
		\hline
		\textbf{Input} & Date & Manufacturer & Model & Engine & &  \\
		\hline
		\textbf{Output} & & & & & Measurement & Part \\
		\hline
	\end{tabular}
	}
	\caption{Example SSQ Model.}
	\label{tab:ssq_example}
\end{table}

The \emph{Query Resolution Method} (QRM) is a data structure that models the question answering process. A QRM represents a generalized executable realization of the search process that the path-finder followed. The QRM is able to reconstruct the page search path followed by the path-finder. Each QRM contains an \emph{ontological realm}, an SSQ, and information to support the query answering process. For each dynamic page, the QRM contains a list of inputs to the URL such as form inputs and the possible reference outputs.

@@

Queries inserted by path-followers take a different approach. The Morpheus search process parses and tags queries in order to record important terms. The system assigns the most probable realm given the terms in the query as calculated from realm-specific copora. Once the realm is assigned, an ontology search is performed to assign classes to the terms. An SSQ is constructed and the system attempts to match this candidate SSQ to existing QRM SSQs. Rather than matching exact query terms, the system matches input and output classes, because a QRM can potentially answer similar queries.

@@

Suppose we want to find the category divergence between \textit{Bus} and \textit{Sedan} (Figure \ref{fig:vehicular_ontology}). \textit{Sedan} is a subcategory of \textit{Automobile}, and \textit{Bus} is a subcategory of \textit{Land\_Vechicle}. Therefore, the least common ancestor ($C$) for these two is \textit{Land\_Vechicle}. In addition, the tree height \textit{h = 4}. So, the normalized divergence $cd$\textit{(Bus, Sedan)} is \textit{0.5} that is calculated from \textit{d(Bus, Root) = 3}, \textit{d(Bus, Land\_Vehicle) = 1}, and \textit{d (Sedan, Land\_Vehicle) = 2}.

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.90]{OntologyDiagram.png}
	\caption{Abbreviated Vehicular Ontology}
	\label{fig:vehicular_ontology}
\end{figure}
